### 2014-05-02 mr_background.tex
small typo

\subsection{MR Imaging in Prostate Diagnostics}
MR imaging has been available for use in the workup of patients with PCa since
the early 1980s, but the early work on its diagnostic accuracy is heterogeneous
due to heavy reliance on morphology via T1 and T2-weighted imaging (T2WI). More
recent abilities to include not only anatomic, but also biologic and functional
dynamic parameters, into MR analysis via diffusion-weighted imaging (DWI),
dynamic contrast-enhanced (DCE) imaging or MR spectroscopic imaging (MRSI) are
promising in the future diagnosis and characterization of PCa.

>>>>

\subsection{MR Imaging in Prostate Diagnostics}
MR imaging has been available for use in the workup of patients with PCa since
the early 1980s, but the early work on its diagnostic accuracy is heterogeneous
due to heavy reliance on morphology via T1- and T2-weighted imaging (T2WI). More
recent abilities to include not only anatomic, but also biologic and functional
dynamic parameters, into MR analysis via diffusion-weighted imaging (DWI),
dynamic contrast-enhanced (DCE) imaging or MR spectroscopic imaging (MRSI) are
promising in the future diagnosis and characterization of PCa.
